---
title: "The Champion is Here"
subtitle: "Predicting the 2024 College Football Playoff Bracket"
author: "Sarah Deussing, Drew Duffy, Adam El-Kadi, Jacob Kowal, and Mitch Jeter"
date: "2024-12-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## College Football Data
2015 - 2024
```{r}
library(cfbfastR)
data <- load_cfb_pbp(2015:2024)
head(data)
#save(data, file = "data2015_2024.RData")
```


```{r}
teams <- c("Oregon", "Penn State", "Notre Dame", "Georgia", "Clemson", "SMU", "Texas", "Tennessee", "Indiana", "Boise State", "Ohio State", "Arizona State")
playoff_teams <- data[data$pos_team %in% teams | data$def_pos_team %in% teams ,]

library(dplyr)
playoff_teams <- playoff_teams %>%
  select(season, game_id, pos_team, def_pos_team, down, down_end, distance, distance_end, yards_gained, EPA, wpa, penalty_detail, turnover, home, away, offense_play, defense_play, offense_conference, defense_conference, yds_rushed, yds_receiving, yds_sacked, yds_fg, completion, punt, fg_made, fg_make_prob, penalty_flag, yds_penalty, play_type, stuffed_run, def_EPA,) %>%
  filter(!is.na(season))
```

Offensive & Defensive Statistics
```{r}
playoff_teams <- playoff_teams %>%
  mutate(fg_difficulty = ifelse(fg_made == TRUE, yds_fg / fg_make_prob, 0),
         conversion4th = ifelse(down == 4 & down_end == 1, 1, ifelse(down == 4 & down_end == 4, 0, NA)),
         conversion3rd = ifelse(down == 3 & down_end == 1, 1, ifelse(down == 3 & down_end == 4, 0, NA)))

# Offense
off_stats <- playoff_teams %>% group_by(pos_team, season, game_id) %>%
 # filter(pos_team %in% teams) %>%
  summarize(avg_EPA = mean(EPA, na.rm = TRUE),
            avg_WPA = mean(wpa, na.rm = TRUE),
            total_rush_yds = sum(yds_rushed, na.rm = TRUE),
            total_rec_yds = sum(yds_receiving, na.rm = TRUE),
            avg_fg_difficulty = mean(fg_difficulty, na.rm = TRUE),
            total_off_penalties = sum(penalty_flag == TRUE),
            total_turnovers = sum(turnover, na.rm = TRUE),
            total_punts = sum(punt == TRUE),
            avg_conversion4th = sum(conversion4th == 1, na.rm = TRUE)/sum(!is.na(conversion4th), na.rm = TRUE),
            avg_conversion3rd = sum(conversion3rd == 1, na.rm = TRUE)/sum(!is.na(conversion3rd), na.rm = TRUE),
            pass_completion_perc = sum(play_type == 'Pass Reception')/sum(play_type == 'Pass Reception' | play_type == 'Pass Incompletion'),
            tot_pass_td = sum(play_type == 'Passing Touchdown'),
            tot_rush_td = sum(play_type == 'Rushing Touchdown'))

# Defense
def_stats <- playoff_teams %>% group_by(def_pos_team, season, game_id) %>%
  #filter(def_pos_team %in% teams) %>%
  summarize(avg_def_EPA = mean(def_EPA, na.rm = TRUE),
    total_def_penalties = sum(penalty_flag == TRUE),
    total_sacks = sum(play_type == 'Sack'),
    total_stuffed_run = sum(stuffed_run, na.rm = TRUE),
    total_interceptions = sum(play_type == 'Interception Return'))
```

```{r}
combined_stats <- off_stats %>%
  left_join(def_stats, by = c("game_id" = "game_id", "pos_team" = "def_pos_team", "season" = "season")) %>%
  rename(team = pos_team) %>%
  arrange(game_id, team)
#combined_stats <- combined_stats %>%
 # filter(team %in% teams)
```

Game Info
```{r}
game_info <- load_cfb_schedules(2015:2024)
game_info <- game_info %>%
  select(game_id, season, home_team, away_team, home_points, away_points) %>%
  mutate(points_diff = home_points - away_points)

# if team in playoff teams won, then win = 1. if team lost, win = 0
game_info <- game_info %>%
  mutate(win = ifelse(home_team %in% teams & points_diff > 0, 1,
                      ifelse(away_team %in% teams & points_diff < 0, 1, 0)),
         win_team = ifelse(points_diff > 0, home_team, away_team))
#unique(game_info$season)
head(game_info)
```

Football Power Index
```{r, eval = FALSE}
library(cfbfastR)
library(httr)
library(jsonlite)

get_fpi_rank_end_of_season <- function(team, year) {
  url <- "https://api.collegefootballdata.com/ratings/fpi"
  api_key <- "V2HgJkz/rPXwIIIjiXX2anIFuXHEpVjicCOvTgxV6phHg4xTooM1BSLQSnMaE2KL"
  
  query <- list(year = year)
  response <- GET(
    url,
    query = query,
    add_headers(
      Accept = "application/json",
      Authorization = paste("Bearer", api_key)
    )
  )
  
  if (status_code(response) == 200) {
    data <- fromJSON(content(response, as = "text"))
    last_game_data <- data %>%
      group_by(team) %>%
      summarize(fpi = last(fpi)) %>%
      arrange(desc(fpi)) %>%
      mutate(rank = row_number())
    team_rank <- last_game_data %>%
      filter(team == !!team) %>%
      select(rank) %>%
      pull(rank)  
    if (length(team_rank) > 0) {
      return(team_rank)
    } else {
      cat("Team not found for the specified year.\n")
    }
  } else {
    cat("Error:", status_code(response), "\n")
    cat("Response content:\n", content(response, as = "text"), "\n")
  }
}

# Input team and year
team <- "Notre Dame"
year <- 2015

rank <- get_fpi_rank_end_of_season(team, year)
if (!is.null(rank)) {
  cat("End-of-season FPI rank for", team, "in", year, "is", rank, "\n")
}

```

```{r, eval = FALSE}
years <- 2015:2024
cfp_teams <- c("Oregon", "Georgia", "Boise State", "Arizona State", "Texas", "Penn State", 
               "Notre Dame", "Ohio State", "Tennessee", "Indiana", "SMU", "Clemson")

get_fpi_rank_end_of_season <- function(team, year) {
  url <- "https://api.collegefootballdata.com/ratings/fpi"
  api_key <- "V2HgJkz/rPXwIIIjiXX2anIFuXHEpVjicCOvTgxV6phHg4xTooM1BSLQSnMaE2KL"

  query <- list(year = year)
  response <- GET(
    url,
    query = query,
    add_headers(
      Accept = "application/json",
      Authorization = paste("Bearer", api_key)
    )
  )

  if (status_code(response) == 200) {
    data <- fromJSON(content(response, as = "text"))
    last_game_data <- data %>%
      group_by(team) %>%
      summarize(fpi = last(fpi)) %>%
      arrange(desc(fpi)) %>%
      mutate(rank = row_number())
    team_rank <- last_game_data %>%
      filter(team == !!team) %>%
      select(rank) %>%
      pull(rank)
    if (length(team_rank) > 0) {
      return(team_rank)
    } else {
      return(NA) # Team not found for the specified year
    }
  } else {
    cat("Error:", status_code(response), "\n")
    cat("Response content:\n", content(response, as = "text"), "\n")
    return(NA) 
  }
}

fpi_ranks <- data.frame(Team = character(), Year = integer(), FPI_Rank = integer(), stringsAsFactors = FALSE)

for (team in cfp_teams) {
  for (year in years) {
    rank <- get_fpi_rank_end_of_season(team, year)
    fpi_ranks <- rbind(fpi_ranks, data.frame(Team = team, Year = year, FPI_Rank = rank))
  }
}

print(fpi_ranks)
write.csv(fpi_ranks, "fpi_ranks.csv", row.names = FALSE)
```

```{r}
fpi <- read.csv('fpi_ranks.csv')
fpi <- fpi %>% rename(team = Team, season = Year)

head(fpi)
```


```{r}
# combine game info
merged <- merge(combined_stats, game_info, by = "game_id", all.x = TRUE)
merged <- merged %>%
  select(-season.y) %>%
  rename(season = season.x) %>%
  filter(!is.na(season))
#unique(merged$season)

# combine fpi
merged <- merge(merged, fpi, by = c("team", "season"))
```

Margins & Favorites/Underdogs
```{r, eval = FALSE}
library(cfbfastR)
library(jsonlite)
library(dplyr)
library(ggplot2)
library(reshape2)
library(tidyr)
library(httr)

# API endpoint
url <- "https://api.collegefootballdata.com/lines?year=2024&seasonType=regular"

# Make the GET request with the API key
response <- GET(url, 
                add_headers(`accept` = "application/json", 
                            `Authorization` = paste("Bearer", api_key)))

# Check response status
if (status_code(response) == 200) {
  # Parse response if successful
  data <- content(response, as = "parsed", simplifyVector = TRUE)
  dataframe <- as.data.frame(data)
  print(head(dataframe))
} else {
  # Print error message
  print(paste("Error:", status_code(response)))
  print(content(response, as = "text"))
}


# Extract the 'spread' column from each element of the 'lines' list
spreads <- lapply(dataframe$lines, function(x) x$spread)

dataframe$spread <- sapply(dataframe$lines, function(x) x$formattedSpread[1])


line15 <- dataframe %>% 
  filter(spread != c("NULL")) %>% 
  select(-lines)


library(stringr)

# Assuming the spread column looks like "Wyoming -13"
line15$favorite_team <- str_extract(line15$spread, "^[^-]+")  # Extracts the team name
line15$favorite_points <- as.numeric(str_extract(line15$spread, "-?\\d+"))


line16 <- dataframe %>% 
  filter(spread != c("NULL")) %>% 
  select(-lines)

line16$favorite_team <- str_extract(line16$spread, "^[^-]+")  # Extracts the team name
line16$favorite_points <- as.numeric(str_extract(line16$spread, "-?\\d+"))


line17 <- dataframe %>% 
  filter(spread != c("NULL")) %>% 
  select(-lines)

line17$favorite_team <- str_extract(line17$spread, "^[^-]+")  # Extracts the team name
line17$favorite_points <- as.numeric(str_extract(line17$spread, "-?\\d+"))

line18 <- dataframe %>% 
  filter(spread != c("NULL")) %>% 
  select(-lines)

line18$favorite_team <- str_extract(line18$spread, "^[^-]+")  # Extracts the team name
line18$favorite_points <- as.numeric(str_extract(line18$spread, "-?\\d+"))

line19 <- dataframe %>% 
  filter(spread != c("NULL")) %>% 
  select(-lines)

line19$favorite_team <- str_extract(line19$spread, "^[^-]+")  # Extracts the team name
line19$favorite_points <- as.numeric(str_extract(line19$spread, "-?\\d+"))

line20 <- dataframe %>% 
  filter(spread != c("NULL")) %>% 
  select(-lines)

line20$favorite_team <- str_extract(line20$spread, "^[^-]+")  # Extracts the team name
line20$favorite_points <- as.numeric(str_extract(line20$spread, "-?\\d+"))


combined_data <- rbind(line17, line18, line19, line20)

# Write the combined_data to a CSV file
write.csv(combined_data, "C://Users/Drew Duffy/Downloads/combined_data.csv", row.names = FALSE)

library(httr)
library(dplyr)
library(stringr)

# Function to get data for a given year and process it
get_season_data <- function(year, api_key) {
  # Construct the URL for the specified year
  url <- paste0("https://api.collegefootballdata.com/lines?year=", year, "&seasonType=regular")
  
  # Make the GET request with the API key, set a timeout of 60 seconds
  response <- GET(url, 
                  add_headers(`accept` = "application/json", 
                              `Authorization` = paste("Bearer", api_key)),
                  timeout(60))  # Increased timeout to 60 seconds
  
  # Check response status
  if (status_code(response) == 200) {
    # Parse response if successful
    data <- content(response, as = "parsed", simplifyVector = TRUE)
    dataframe <- as.data.frame(data)
    
    # Extract the 'spread' column from each element of the 'lines' list
    dataframe$spread <- sapply(dataframe$lines, function(x) x$formattedSpread[1])
    
    # Filter rows where the spread is not NULL
    line15 <- dataframe %>% 
      filter(spread != "NULL") %>% 
      select(-lines)
    
    # Use stringr to extract favorite team and points
    line15$favorite_team <- str_extract(line15$spread, "^[^-]+")  # Extracts the team name
    line15$favorite_points <- as.numeric(str_extract(line15$spread, "-?\\d+"))
    
    return(line15)
  } else {
    # Print error message
    print(paste("Error:", status_code(response)))
    print(content(response, as = "text"))
    return(NULL)
  }
}

# Initialize an empty list to store data for each season
all_seasons_data <- list()

# Loop over the years from 2015 to 2024
for (year in 2015:2024) {
  print(paste("Processing year:", year))
  season_data <- get_season_data(year, api_key)
  if (!is.null(season_data)) {
    # Add the season data to the list
    all_seasons_data[[as.character(year)]] <- season_data
  }
}

# Combine all the season data into a single dataframe
margin_data <- bind_rows(all_seasons_data)

# View the combined data

# Optionally, save the combined data to a CSV file
write.csv(margin_data, "combined_season_data.csv", row.names = FALSE)


margin_data <- margin_data %>%
  mutate(
    favorite_score = case_when(
      favorite_team == homeTeam ~ homeScore,
      favorite_team == awayTeam ~ awayScore,
      TRUE ~ NA_real_
    ),
    underdog_score = case_when(
      favorite_team == homeTeam ~ awayScore,
      favorite_team == awayTeam ~ homeScore,
      TRUE ~ NA_real_
    )
  )


head(margin_data[, c("favorite_team", "homeTeam", "awayTeam")])
margin_data$favorite_team <- as.character(margin_data$favorite_team)
margin_data$homeTeam <- as.character(margin_data$homeTeam)
margin_data$awayTeam <- as.character(margin_data$awayTeam)

margin_data <- margin_data %>%
  mutate(
    favorite_score = case_when(
      tolower(trimws(favorite_team)) == tolower(trimws(homeTeam)) ~ homeScore,
      tolower(trimws(favorite_team)) == tolower(trimws(awayTeam)) ~ awayScore,
      TRUE ~ NA_real_
    ),
    underdog_score = case_when(
      tolower(trimws(favorite_team)) == tolower(trimws(homeTeam)) ~ awayScore,
      tolower(trimws(favorite_team)) == tolower(trimws(awayTeam)) ~ homeScore,
      TRUE ~ NA_real_
    )
  )

# Check the output to verify the new columns
head(margin_data[, c("favorite_team", "homeTeam", "awayTeam", "favorite_score", "underdog_score")])

str(margin_data$homeScore)
str(margin_data$awayScore)

margin_data$homeScore <- as.numeric(margin_data$homeScore)
margin_data$awayScore <- as.numeric(margin_data$awayScore)

margin_data$favorite_score_diff <- as.numeric(margin_data$favorite_score - margin_data$underdog_score)
margin_data$fav_margin <- as.numeric(margin_data$favorite_points - -(margin_data$favorite_score_diff))
margin_data$dog_margin <- as.numeric(margin_data$favorite_points - -(margin_data$favorite_score_diff)) * -1




margin_data <- margin_data %>% 
  filter(!is.na(margin))

margin_data <- margin_data %>%
  mutate(
    underdog_team = case_when(
      tolower(trimws(favorite_team)) == tolower(trimws(homeTeam)) ~ awayTeam,  # if favorite_team is homeTeam, underdog is awayTeam
      tolower(trimws(favorite_team)) == tolower(trimws(awayTeam)) ~ homeTeam,  # if favorite_team is awayTeam, underdog is homeTeam
      TRUE ~ NA_character_  # if neither condition is met (shouldn't happen with valid data)
    )
  )

# Check the output to verify the new underdog_team column
head(margin_data[, c("favorite_team", "homeTeam", "awayTeam", "underdog_team")])


favorite_margins <- margin_data %>% group_by(favorite_team, season) %>% 
  summarise(favorite_margin = sum(fav_margin, na.rm = TRUE)) %>% 
  rename(team = favorite_team) %>% 
  mutate(season = as.factor(season))

underdog_margins <- margin_data %>% group_by(underdog_team, season) %>% 
  summarise(underdog_margin = sum(dog_margin, na.rm = TRUE)) %>% 
  rename(team = underdog_team) %>% 
  mutate(season = as.factor(season)) 

favorite_margins$team <- trimws(favorite_margins$team) 
underdog_margins$team <- trimws(underdog_margins$team) 
total_margins <- full_join(favorite_margins, underdog_margins, by = c("team", "season")) 


total_margins <- total_margins %>% 
  mutate(favorite_margin = ifelse(is.na(favorite_margin), 0, favorite_margin), 
         underdog_margin = ifelse(is.na(underdog_margin), 0, underdog_margin)) 


write.csv(total_margins, "C://Users/Drew Duffy/Downloads/total_margins.csv", row.names = FALSE)
```

```{r}
margins <- read.csv('total_margins.csv')
merged <- merge(merged, margins, by = c('team', 'season'))

head(margins)
```

Weather & Temperature Difference
```{r}
weather <- read.csv('cfb_weather_2015_2024.csv')
weather <- weather %>%
  select(game_id, season, home_team, temperature)

# average team weather = yearly average temp for that team's home stadium
avg_team_weather <- weather %>% group_by(season, home_team) %>%
  summarize(avg_temp = mean(temperature, na.rm = TRUE))

# for merge: if team == home_team, temp_diff = 0
# else: temp_diff = get the weather for that team and subtract it from home team's weather
merged3 <- merged %>%
  left_join(weather, by = c("season", "game_id"))

merged3 <- merged3 %>%
  mutate(temp_diff = ifelse(home_team.y == team, 0,
                            temperature - avg_team_weather[avg_team_weather$home_team == away_team &
                                               avg_team_weather$season == season, ]$avg_temp))
```


## XGBoost Modeling

Fill any NA values with zeros
```{r}
summary(merged)
# fill all NAs with 0
merged2 <- merged3 %>% mutate_all(~replace(., is.na(.), 0))
sum(is.na(merged2))

merged2$win_team_binary <- ifelse(merged2$win_team == merged2$team, 1, 0)

train_data <- merged2 %>% filter(season >= 2015 & season <= 2023)
#sum(is.na(train_data))
test_data <- merged2 %>% filter(season == 2024)
```

Training data: 2015-2023
```{r}
#colnames(merged2)
features <- c("avg_EPA", "avg_WPA", "total_rush_yds", "total_rec_yds", "avg_fg_difficulty", "total_off_penalties", "total_turnovers", "total_punts", "avg_conversion4th", "avg_conversion3rd", "pass_completion_perc", "tot_pass_td", "tot_rush_td", "avg_def_EPA", "total_def_penalties", "total_sacks", "total_stuffed_run", "total_interceptions", "FPI_Rank", "favorite_margin", "underdog_margin", "temp_diff")

X_train <- train_data %>% select(all_of(features)) %>% as.matrix()
y_train <- train_data$win_team_binary
```

Test data: Predict for 2024 regular season data
```{r}
library(xgboost)

xgb_model <- xgboost(
  data = X_train, 
  label = y_train,
  objective = "binary:logistic",  
  eval_metric = "auc",       
  nrounds = 1000,  
  early_stopping_rounds = 50,
  max_depth = 20,              
  eta = 0.1,            
  gamma = 0,                     
  colsample_bytree = 0.8,        
  subsample = 0.8,
  verbose = 0
)

X_test <- test_data %>% select(all_of(features)) %>% as.matrix()
y_pred_prob <- predict(xgb_model, X_test)

y_pred_class <- ifelse(y_pred_prob > 0.5, 1, 0)
test_data$predicted_win_binary <- y_pred_class

test_data <- test_data %>%
  group_by(game_id) %>%
  mutate(predicted_win_team = ifelse(predicted_win_binary == 1, team, NA)) %>%
  ungroup()

test_data_winner <- test_data %>%
  group_by(game_id) %>%
  summarise(predicted_game_winner = first(predicted_win_team[!is.na(predicted_win_team)])) %>%
  ungroup()

final_predictions <- left_join(test_data, test_data_winner, by = "game_id")

final_predictions$predicted_win_team <- ifelse(final_predictions$predicted_win_binary == 1, final_predictions$team, 
                                               ifelse(final_predictions$team == final_predictions$home_team, final_predictions$away_team, final_predictions$home_team))

accuracy <- mean(final_predictions$predicted_win_team == final_predictions$win_team) ## 0.882
```

Feature Importance
```{r}
importance_matrix <- xgb.importance(model = xgb_model)
#xgb.plot.importance(importance_matrix)
#print(importance_matrix)
```

```{r}
library(ggplot2)
importance_matrix_df <- data.frame(
  Feature = importance_matrix$Feature,
  Gain = importance_matrix$Gain,
  Frequency = importance_matrix$Frequency,
  Cover = importance_matrix$Cover
)

importance_matrix_df <- importance_matrix_df %>%
  arrange(desc(Gain))

importance_matrix_df$Top_Three <- ifelse(importance_matrix_df$Feature %in% importance_matrix_df$Feature[1:3], "Top 3", "Other")

ggplot(importance_matrix_df, aes(x = reorder(Feature, Gain), y = Gain, fill = Top_Three)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  scale_fill_manual(values = c("Top 3" = "red", "Other" = "gray")) +
  coord_flip() +  # Flip coordinates for horizontal bars
  labs(title = "Feature Importance", x = "Features", y = "Gain") +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10),
        plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
  panel.grid = element_blank())


```

## Predict Playoffs

Function to simulate playoff game: summarize 2024 data for matchup teams.
```{r}
predict_game_winner <- function(team_1, team_2, game_stats_2024, xgb_model, features) {
  team_1_stats <- game_stats_2024 %>%
    filter(season == 2024 & team == team_1)
  
  team_2_stats <- game_stats_2024 %>%
    filter(season == 2024 & team == team_2)

  team_1_avg_stats <- team_1_stats %>%
    summarise(across(all_of(features), mean, na.rm = TRUE))
  
  team_2_avg_stats <- team_2_stats %>%
    summarise(across(all_of(features), mean, na.rm = TRUE))

  game_prediction_data <- bind_rows(team_1_avg_stats, team_2_avg_stats) %>%
    mutate(team = c(team_1, team_2))
  game_pred2 <- game_prediction_data
  colnames(game_pred2) <- features
  rownames(game_pred2) <- c(team_1, team_2)
  
  game_matrix <- as.matrix(game_prediction_data %>% select(-team))
  
  y_pred_prob <- predict(xgb_model, game_matrix)

  predicted_winner <- ifelse(y_pred_prob[1] > y_pred_prob[2], team_1, team_2)
  
  return(list(predicted_winner = predicted_winner, game_pred2 = game_pred2))
}
```

Simulate Bracket
```{r}
# First round:
winner7_10 <- predict_game_winner("Notre Dame", "Indiana", merged2, xgb_model, features)$predicted_winner
print(paste0("Notre Dame v. Indiana: ", winner7_10))
game7_10 <- predict_game_winner("Notre Dame", "Indiana", merged2, xgb_model, features)$game_pred2

winner8_9 <- predict_game_winner("Ohio State", "Tennessee", merged2, xgb_model, features)$predicted_winner
print(paste0("Ohio State v. Tennessee: ", winner8_9))
game8_9 <- predict_game_winner("Ohio State", "Tennessee", merged2, xgb_model, features)$game_pred2

winner5_12 <- predict_game_winner("Texas", "Clemson", merged2, xgb_model, features)$predicted_winner
print(paste0("Texas v. Clemson: ", winner5_12))
game5_12 <- predict_game_winner("Texas", "Clemson", merged2, xgb_model, features)$game_pred2

winner6_11 <- predict_game_winner("Penn State", "SMU", merged2, xgb_model, features)$predicted_winner
print(paste0("Penn State v. SMU: ", winner6_11))
game6_11 <- predict_game_winner("Penn State", "SMU", merged2, xgb_model, features)$game_pred2

# Second Round
winner1 <- predict_game_winner("Oregon", winner8_9, merged2, xgb_model, features)$predicted_winner
print(paste0("Oregon v. ", winner8_9, ": ", winner1))
game1 <- predict_game_winner("Oregon", winner8_9, merged2, xgb_model, features)$game_pred2

winner2 <- predict_game_winner("Georgia", winner7_10, merged2, xgb_model, features)$predicted_winner
print(paste0("Georgia v. ", winner7_10, ": ", winner2))
game2 <- predict_game_winner("Georgia", winner7_10, merged2, xgb_model, features)$game_pred2

winner3 <- predict_game_winner("Boise State", winner6_11, merged2, xgb_model, features)$predicted_winner
print(paste0("Boise State v. ", winner6_11, ": ", winner3))
game3 <- predict_game_winner("Boise State", winner6_11, merged2, xgb_model, features)$game_pred2

winner4 <- predict_game_winner("Arizona State", winner5_12, merged2, xgb_model, features)$predicted_winner
print(paste0("Arizona State v. ", winner5_12, ": ", winner4))
game4 <- predict_game_winner("Arizona State", winner5_12, merged2, xgb_model, features)$game_pred2

# Semis
winner1_semi <- predict_game_winner(winner1, winner4, merged2, xgb_model, features)$predicted_winner
print(paste0(winner1, " v. ", winner4, ": ", winner1_semi))
game1_semi <- predict_game_winner(winner1, winner4, merged2, xgb_model, features)$game_pred2

winner2_semi <- predict_game_winner(winner2, winner3, merged2, xgb_model, features)$predicted_winner
print(paste0(winner2, " v. ", winner3, ": ", winner2_semi))
game2_semi <- predict_game_winner(winner2, winner3, merged2, xgb_model, features)$game_pred2

# Champion
champion <- predict_game_winner(winner1_semi, winner2_semi, merged2, xgb_model, features)$predicted_winner
print(paste0("Champion 2024: ", champion))
champ_game <- predict_game_winner(winner1_semi, winner2_semi, merged2, xgb_model, features)$game_pred2

#predict_game_winner("Penn State", "Ohio State", merged2, xgb_model)
```

Combine team data for comparison
```{r}
playoff_stats_output <- rbind(game5_12, game6_11, game7_10, game8_9, game1, game2, game3, game4, game1_semi, game2_semi, champ_game)
#write.csv(playoff_stats_output, 'playoff_stats_output.csv')
playoff_stats_output
```

